A Note on the Period Enforcer Algorithm for Self-Suspending Tasks

### 2015-10-17 LITES/LITES-Paper.tex
Some minor polishing and shuffling around of the figures
proofreading fixes and tweaks
add discussion of first locking counterexample
restructure for sync with Authorea
try another way
add subject classification

\title{A Note on the Period Enforcer Algorithm  for Self-Suspending Tasks}

\author[1]{Jian-Jia Chen}
\author[2]{Bj\"orn Brandenburg}
\affil[1]{TU Dortmund University, Germany\\
  \texttt{jian-jia.chen@cs.uni-dortmund.de}}
\affil[2]{Max Planck Institute for Software Systems (MPI-SWS)\\
  \texttt{bbb@mpi-sws.org}}
\authorrunning{Chen and Brandenburg} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'

@@

%\subjclass{MANDATORY:  Please refer to \url{www.acm.org/about/class/2012}}% mandatory: Please choose 2012 ACM classifications from http://www.acm.org/about/class/2012 . E.g., cite as "Integrated circuits". 
%\keywords{MANDATORY: Please provide 1--5 keywords as a comma-separated list}% mandatory: Please provide 1-5 keywords
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\maketitle
\input{../abstract.tex}
\input{../untitled.tex}
\begin{figure}[t]
  \centering
  \input{../figures/example-original/example-body.tex}
  \caption{An illustrative example of the original self-suspending task schedule.}
  \label{fig:example-original}
  \end{figure}

\begin{figure}[t]
  \centering
  \input{../figures/example/example-body.tex}
  \caption{An illustrative example demonstrating a deadline miss at time 22
    under the period enforcer algorithm.}
\label{fig:example}  
\end{figure}
%\input{../figures/example-original/example.png}
%\input{../figures/example/example.png}
\input{../transformation.tex}
\input{../conclusion.tex}

>>>>

\papertrue 
\title{A Note on the Period Enforcer Algorithm  for Self-Suspending Tasks}

\author[1]{Jian-Jia Chen}
\author[2]{Bj\"orn B.\ Brandenburg}
\affil[1]{TU Dortmund University, Germany\\
  \texttt{jian-jia.chen@cs.uni-dortmund.de}}
\affil[2]{Max Planck Institute for Software Systems (MPI-SWS)\\
  \texttt{bbb@mpi-sws.org}}
\authorrunning{Chen and Brandenburg} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'

@@

\subjclass{Real-time systems, Real-time schedulability, Synchronization}% mandatory: Please choose 2012 ACM classifications from http://www.acm.org/about/class/2012 . E.g., cite as "Integrated circuits". 
\keywords{period enforcer, deferred execution, self-suspension, blocking}% mandatory: Please provide 1-5 keywords
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\maketitle
\input{../abstract.tex}
\input{../untitled.tex}

%\input{../figures/example-original/example.png}
%\input{../figures/example/example.png}
\input{../transformation.tex}
\input{../locking.tex}
\input{../conclusion.tex}
